\simname 2.0 User's Guide

### 2010-03-09 doc/manual.tex
update book sim manual
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@1768 ce7aba0d-9f81-40a6-a495-cecae84b0515

\subsubsection{Injection mode}
The rate at which packets are injected into the simulator is set using
the \texttt{injection\_rate} option.  The simulator's cycle time is a
flit cycle, the time it takes a single flit to be injected at a
source, and the injection rate is specified in packets per flit cycle\footnote{The unit of \texttt{injection\_rate} can be changed to flits per cycle by setting \texttt{injection\_rate\_uses\_flits} to 1.}.
For example, setting \texttt{injection\_rate = 0.25} means that each
source injects a new packet in one out of every four simulator cycles.

@@

Alternatively, the simulator can be configured to generate request-reply traffic. In this mode, the traffic manager injects read and write requests into the network; when a destination node receives such a request packet, it returns a reply packet of the same type\footnote{Injection of reply packets has priority over injection of new requests packets.}. Consequently, the effective overall network load is generated by both the injected requests and the automatically generated replies. Request-reply traffic ignores the \texttt{const\_flits\_per\_packet} option; instead, packet sizes are determined by the \texttt{\{read|write\}\_\{request|reply\}\_size} options. Furthermore, the mapping of packet types to VCs can be customized using the \texttt{\{read|write\}\_\{request|reply\}\_\{begin|end\}\_vc} options.

>>>>

\subsubsection{Injection mode}
The rate at which packets are injected into the simulator is set using
the \texttt{injection\_rate} option.  The simulator's cycle time is a
flit cycle, the time it takes a single flit to be injected at a
source, and the injection rate is specified in packets per flit cycle.
For example, setting \texttt{injection\_rate = 0.25} means that each
source injects a new packet in one out of every four simulator cycles.
The unit of \texttt{injection\_rate} can optionally be changed to flits per cycle by 
setting \texttt{injection\_rate\_uses\_flits} to 1.

@@

Alternatively, the simulator can be configured to generate request-reply 
traffic. In this mode, the traffic manager injects read and write requests 
into the network; when a destination node receives such a request 
packet, it returns a reply packet of the same type. Injection of reply 
packets has priority over injection of new requests packets. 
Consequently, the effective overall network load is generated by both 
the injected requests and the automatically generated replies. 
Request-reply traffic ignores the \texttt{const\_flits\_per\_packet} 
option; instead, packet sizes are determined by the 
\texttt{\{read|write\}\_\{request|reply\}\_size} options. Furthermore, 
the mapping of packet types to VCs can be customized using the 
\texttt{\{read|write\}\_\{request|reply\}\_\{begin|end\}\_vc} options.
